\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{enumitem}

% --- Branding Colors ---
\definecolor{AetherLavender}{HTML}{7663b0}
\definecolor{AetherDark}{HTML}{0a0a0c}

% --- Page Setup ---
\geometry{
    margin=2cm
}

% --- Custom Sections ---
\titleformat{\section}{\Large\bfseries\color{AetherLavender}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

% --- Hyperlink Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=AetherLavender,
    filecolor=magenta,      
    urlcolor=AetherLavender,
}

\begin{document}

\begin{center}
    {\Huge \textbf{Aether Ecosystem}}\\[1em]
    {\Large \textit{One Platform. Six Powerhouses. Zero Compromise.}}\\[2em]
    {\large Comprehensive Platform Architecture and Features Documentation}\\[1em]
    \today
\end{center}

\vspace{2em}
\tableofcontents
\newpage

\section{Executive Summary}
The Aether Ecosystem is an enterprise-grade, AI-native unified business platform that consolidates six mission-critical operational domains---Supply Chain, CRM, Document Intelligence, Tax \& Compliance, Autonomous Sales Development, and WhatsApp Commerce---into a single, cohesive deployment. Designed explicitly for the Indian B2B SMB market, it features a pitch-black glassmorphism user interface with signature lavender accents, delivering a premium workspace powered continuously by Google Gemini 3.1 Flash Lite Preview.

\section{The Core Philosophy: A Unified Architecture}
Rather than connecting disparate SaaS solutions via fragile API integrations, Aether operates as a single source of truth. 
Data collected in the warehouse feeds directly into CRM client health scores; extracted invoice data seamlessly cross-references with GSTR-2B compliance; and the AI Sales Development Rep utilizes live inventory data to prioritize outreach.

\section{The Six Powerhouses}

\subsection{1. Aether Supply (Supply Chain Intelligence)}
The foundational layer of the ecosystem, providing complete inventory, purchasing, and warehouse management operations.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Inventory & Product Management:} Full tracking of SKUs, pricing (cost/sell), and auto-classification of stock health (Critical/Low/Healthy/Overstocked). Includes bulk CSV imports and browser-based barcode scanning.
    \item \textbf{Warehouse Operations:} Multi-location tracking with capacity utilization metrics, intuitive stock transfers, and a Three.js-powered 3D visualization of the warehouse floor.
    \item \textbf{AI Forecasting & Anomalies:} Real-time ingestion of sales history allowing Gemini to generate exponential smoothing forecasts and anomaly alerts (detecting unusual demand spikes or inventory drops).
    \item \textbf{Intelligent Purchasing:} Algorithmic "Smart Reorder" calculates safety stock and order points, automatically drafting Purchase Orders for approved suppliers.
\end{itemize}

\subsection{2. AetherCRM (Customer Relationship Management)}
A high-velocity sales management tool focused on pipeline clarity and client intelligence.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Pipeline Management:} Kanban-style board tracking deals from Lead to Won, displaying real-time revenue velocity.
    \item \textbf{Client Directory & Geo-mapping:} Comprehensive client records coupled with geographic plotting for territory sales visualization.
    \item \textbf{AI Smart Quotes:} Instantly generates customized, professional quotes drawing directly from live Aether Supply inventory availability and pricing.
    \item \textbf{Email Drafter:} Context-aware outbound email generation that analyzes client history to personalize communication.
\end{itemize}

\subsection{3. AetherDocs (Intelligent Document Processing)}
Transforms unstructured paperwork into structured data and automates outbound document creation.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Document Extraction:} Utilizes Gemini 3.1 Flash Lite to parse uploaded PDFs/images (invoices, receipts, POs), extracting structured line items, GST numbers, and vendor details automatically.
    \item \textbf{Library \& Export:} Processed documents are stored with confidence scores and can be exported cleanly to JSON or CSV arrays.
    \item \textbf{Invoice \& PO Builder:} A robust templating engine enabling manual or prompt-based AI generation of professional documents, subsequently rendered as branded PDFs via React-PDF.
\end{itemize}

\subsection{4. AetherTax (GST \& Compliance Intelligence)}
Designed specifically for Indian regulatory standards, this module handles the complexities of GST reconciliation.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Automated Reconciliation:} Performs complex side-by-side matching of internal purchase records (Books) against government portal data (GSTR-2B).
    \item \textbf{Mismatch Identification:} Quickly flags discrepancies natively (e.g., Missing in Portal, Delta in Amount).
    \item \textbf{AI Advisory Generation:} Feeds mismatched data to the LLM to output a Chartered Accountant (CA) grade markdown advisory, outlining exact lost Input Tax Credit (ITC) and recommended actions.
    \item \textbf{Direct CA Alerting:} Instantly share compliance reports with accounting teams via one-click messaging workflows.
\end{itemize}

\subsection{5. AetherSDR (AI Sales Development Representative)}
An autonomous top-of-funnel agent designed to prospect, qualify, and book meetings.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Lead Sourcing \& Scoring:} Aggregates prospects (e.g., via Apollo/LinkedIn integration placeholders) and applies a 0-100 qualification score.
    \item \textbf{Multi-Channel Cadences:} Visual builder for email and WhatsApp outreach sequences incorporating branching logic based on prospect replies.
    \item \textbf{Gemini Contextual Drafting:} Dynamically writes initial outreach and follow-up emails based on scraped prospect pain points and role descriptions.
    \item \textbf{Meeting Scheduling:} Integration points for Calendar scheduling, seamlessly handing qualified leads down to human reps in the AetherCRM pipeline.
\end{itemize}

\subsection{6. AetherCommerce (WhatsApp AI Commerce Agent)}
A comprehensive conversational commerce hub acting as the primary digital interface for the company's customers.
\begin{itemize}[label=\textcolor{AetherLavender}{\textbullet}]
    \item \textbf{Multilingual Catalog \& Support:} Autonomous handling of customer queries, order tracking, and product catalogs in English, Hindi, Marathi, and Gujarati.
    \item \textbf{Transaction Handling:} Native handling of cart creation and triggering UPI payment links.
    \item \textbf{Human Operations Inbox:} A dedicated dispatch inbox where the AI agent pauses execution and explicitly hands off complex/frustrated conversational threads to a human administrator.
    \item \textbf{Broadcast Campaigns:} Send targeted, auto-localized promotional templates to granular CRM segments.
\end{itemize}

\section{Technical Infrastructure}

The ecosystem runs on a highly modern, scalable technology stack:

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\textwidth}{l X}
\toprule
\textbf{Layer} & \textbf{Technology} \\
\midrule
\textbf{Frontend Framework} & Next.js 15 (App Router) \\
\textbf{UI/UX} & React 19, Tailwind CSS 4, Framer Motion 12, Lucide Icons \\
\textbf{Data Visualization} & Recharts 3, Three.js (for warehouse) \\
\textbf{Database \& ORM} & Prisma 5, Supabase/Neon PostgreSQL (with local SQLite dev support) \\
\textbf{Intelligence Core} & Google GenAI SDK powered by \texttt{gemini-3.1-flash-lite-preview} \\
\textbf{Document Generation}& React-PDF / pdf-lib \\
\bottomrule
\end{tabularx}
\end{table}

\section{Security and Access Architecture}

Because a centralized system holds all corporate data, access is strictly governed. 
Authentication is managed via a centralized \texttt{AuthProvider} context that verifies user sessions. Permissions are enforced per-module based on assigned Role Metadata (\texttt{ROLE\_META}). An inventory manager, for example, can be granted unfettered access to \texttt{Aether Supply} while being strictly compartmentalized away from \texttt{AetherTax}.

\vspace{2em}
\begin{center}
\textit{End of Documentation}
\end{center}

\end{document}
